### 2024-01-23 iterative_monomorphisation.tex
started adding tables

\usepackage{soul}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsmath}

@@

@@

>>>>

\usepackage{soul}
\usepackage{caption}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsmath}

@@

\break

@@

\break

\begin{center}
\captionof{table}{Bounds and options to test}
\begin{tabular}{ccccc}
   \toprule
   \multicolumn{5}{c}{monomorphisation point (steps)} \\
   0 & 25 & 50 & 100 & 200 \\
   \midrule
   \multicolumn{4}{c}{new clauses multiplier} \\
   1.0 & 1.5 & 2.0 & 3.0 \\
   \midrule
   \multicolumn{3}{c}{total new clauses cap} \\
   2000 & 5000 & none\\
   \midrule
   \multicolumn{4}{c}{loop number} \\
   2 & 3 & 4 & 5 \\
   \midrule
   \multicolumn{5}{c}{monomorphisation point (steps)} \\
   0 & 25 & 50 & 100 & 200 \\

   \bottomrule
\end{tabular}
\end{center}

\begin{center}
\captionof{table}{Monomorphisation to the service of Zipperposition?}
\begin{tabular}{lccc}
   \toprule
   &portfolio classic & portfolio monomorphisation & custom portfolio \\
   \midrule
   bounds  & -  & - & - \\
   bounds2 & - & - & - \\
   bounds3 & - & - & - \\
   bounds4 & - & - & - \\
   bounds5 & - & - & - \\

   \bottomrule
\end{tabular}
\end{center}

\bigskip
\bigskip
\bigskip

\begin{center}
\captionof{table}{Monomorphisation as an alternative to native polymorphism?}
\begin{tabular}{lccccccccc}
   \toprule
   & \multicolumn{2}{c}{E}   & \multicolumn{2}{c}{Vampire} &\multicolumn{2}{c}{Leo3} & \multicolumn{2}{c}{Satallax} \\
   \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9}
   & native & mono & native & mono & native & mono & native & mono\\
   \midrule
   bounds  & - & - & - & - & - & - & - & - \\
   bounds' & - & - & - & - & - & - & - & - \\
   bounds* & - & - & - & - & - & - & - & - \\
   bounds? & - & - & - & - & - & - & - & - \\
   \bottomrule
\end{tabular}
\end{center}

\break
